A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-04-29 paper_selecta.tex
minor fix

\end{tikzpicture}
\end{adjustbox}
\caption{This figure shows the orbits of square-zero supercharges in each dimension, and how they relate to one another under dimensional reduction.  The labels indicate each orbit: the number refers to the rank, and the subscript indicates the situations where the supercharges of a given rank split into multiple orbits.  Each column is labelled by a dimension, and each row by the number of invariant directions of the supercharge.  Colours indicate the maximal supersymmetry algebra where the given supercharges live, so red indicates supercharges defined in algebras with 16 supercharges, orange those with 8 supercharges, and yellow those with 4 supercharges.  There is an arrow whenever one twist dimensionally reduces to another twist one dimension lower.}
\label{fig:superchargeorbits}
\end{figure}

>>>>

\end{tikzpicture}
\end{adjustbox}
\caption{This figure shows the orbits of square-zero supercharges in each dimension, and how they relate to one another under dimensional reduction.  The labels indicate each orbit: the number refers to the rank, and the subscript indicates the situations where the supercharges of a given rank split into multiple orbits.  Each column is labelled by a dimension, and each row by the number of invariant directions of the supercharge.  Colours indicate the maximal supersymmetry algebra where the given supercharges live, so black indicates supercharges defined in algebras with 16 supercharges, gray those with 8 supercharges, and white those with 4 supercharges.  There is an arrow whenever one twist dimensionally reduces to another twist one dimension lower.}
\label{fig:superchargeorbits}
\end{figure}
